Twisted 11-dimensional supergravity, I

### 2021-08-25 draft.tex
merge

@@

@@

@@

We start with the global symmetry algebra $E(5,10)$ of the holomorphic twist of the 11-dimensional theory. 
From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
\[
\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
\]
We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.

@@

Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
\[
H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
\]
Notice that on $\CC^2$, there is an exactly sequence of Lie algebras
\[
0 \to \ul\CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
\]
where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$:
\[
[f(z_1,z_2) , g(z_1,z_2)] = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
\]

>>>>

\begin{thm}
There is a map of super Lie algebras from the super Lie algebra $E^{hol}(5,10)$ to the Lie algebra of gauge symmetries of the 11-dimensional theory on $\CC^5 \times \RR$. 
This map is an embedding at the level of cohomology. 
\end{thm}

\begin{proof}
We define the map directly. 
The even part of $E^{hol}(5,10)$ is precisely the Lie algebra of holomorphic divergence-free vector fields on $\CC^5$. 
We simply embed this in the space $\PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$ of $\mu$-fields in the 11-dimensional theory.

The odd part of $E^{hol}(5,10)$ is the space of holomorphic closed two-forms on $\CC^5$. 
To embed this in the space of fields of the 11-dimensional theory we need to choose primitives. 
We do this by fixing a homotopy $H \colon \Omega^{2,hol}_{cl} (\CC^5) \to \Omega^{1,hol} (\CC^5)$ by
\[
(H \alpha) (z) = \int_{0}^z \alpha .
\]
Since $\alpha$ is closed, one has $\partial H \alpha = \alpha$.
We send $\alpha$ to the $\gamma$-type field $H \alpha$ viewed as an element of $\Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$.

All embedded elements of $E(5,10)$ are $\dbar$, $\d_{\RR}$, and $\div$-closed and so descends to a map in cohomology. 
The first nontrivial Lie bracket compatibility we check is between two $\alpha$-type elements. 
We will do this in coordinates. 
Suppose $f^{ij} \d z_i \wedge \d z_j$, $g^{ij} \d z_i \wedge \d z_j$ are two closed two-forms. 
On one hand, in $E(5,10)$ we have 
\[
[f^{ij} \d z_i \wedge \d z_j, g^{kl} \d z_k \wedge \d z_l] = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} .
\]

On the other hand, in the 11-dimensional theory there is the following Lie bracket between $\gamma$-type fields
\begin{align*}
[H (f^{ij} \d z_i \wedge \d z_j), H(g^{kl} \d z_k \wedge \d z_l)] & = \big(\del H (f^{ij} \d z_i \wedge \d z_j) \wedge \del H(g^{kl} \d z_k \wedge \d z_l) \big) \vee \partial_{z_1} \wedge \cdots \wedge \partial_{z_5} \\
& = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} 
\end{align*}
as desired.

The final Lie bracket compatibility we need to check is between a divergence-free vector field $f_i \partial_{z_i}$ and a closed two-form $g^{ij} \d z_i \wedge \d z_j$. 
In $E(5,10)$ we have
\[
[f_i \partial_{z_i} , g^{kl} \d z_k \wedge \d z_l] = \del (f_i g^{il} \d z_l) . 
\]
This is embedded as the one-form $f_i g^{il} \d z_l$ up to exact terms. 
On the other hand, in the 11-dimensional theory we have the following $[\mu,\gamma]$ type bracket
\begin{align*}
[f_i \partial_{z_i}, H(g^{kl} \d z_k \wedge \d z_l)] & = L_{f_i \partial_{z_i}} H(g^{kl} \d z_k \wedge \d z_l) \\ 
& = \iota_{f_i \partial_{z_i}} g^{kl} \d z_k \wedge \d z_l + \del \iota_{f_i \partial_{z_i}} H g^{kl} \d z_k \wedge \d z_l \\
& = f_i g^{il} \d z_l + \del - \text{exact} .
\end{align*}

@@

\brian{introduce PCS}
Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
\[
\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
\]

@@

The Lie algebra of gauge symmetries of this model on flat space is 
\[
\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
\]
which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$.

@@

Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
\[
\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
\]
We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.

@@

Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
\[
H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
\]
Notice that on $\CC^2$, there is a split exact sequence of Lie algebras
\[
0 \to \CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
\]
where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$.
Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.
